Memes: an R interface to the MEME Suite

### 2021-04-07 manuscript.Rmd
add install chunk for uninstalled packages

```{r setup, echo = FALSE, warning=FALSE, message=FALSE, include=FALSE}
# Figure caption: https://stackoverflow.com/questions/31926623/figures-captions-and-labels-in-knitr
suppressPackageStartupMessages(library(memes))
suppressPackageStartupMessages(library(magrittr))
suppressPackageStartupMessages(library(GenomicRanges))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(ComplexHeatmap))
suppressPackageStartupMessages(library(universalmotif))
# TODO add auto install chunk:
# Need to install: ComplexHeatmap, drake, readxl, gt, bookdown
# version pin these?
drake::r_make()
```

@@

In order to examine the properties of the E93 motif between different ChIP
peaks, we scan all E93 ChIP peaks for matches to the Fly Factor Survey E93 motif
using `runFimo()`. Results are returned as a GRanges object containing the
positions of each motif. Setting `skip_matched_sequence` to `FALSE` adds the
sequence of the detected motif to the output.

```{r}
e93_fimo <- runFimo(all_sequences, fly_factor_expressed$Eip93F_SANGER_10, skip_matched_sequence = FALSE, thresh = 1e-3)
```

@@

This manuscript was automatically generated using Rmarkdown within the
`memes_docker` container. Its source code, raw data, and
instructions to reproduce all analysis can be found at
[github.com/snystrom/memes_paper/](github.com/snystrom/memes_paper/).

>>>>

```{r setup, echo = FALSE, warning=FALSE, message=FALSE, include=FALSE}
# Figure caption: https://stackoverflow.com/questions/31926623/figures-captions-and-labels-in-knitr

# Install pkgs not preinstalled in container
need_install <- c("ComplexHeatmap", "drake", "readxl", "gt", "bookdown")

lapply(need_install, function(x){
  if (!require(x, character.only = TRUE)) {
    BiocManager::install(x, dependencies = TRUE)
  }
})

# Load pkgs
suppressPackageStartupMessages(library(memes))
suppressPackageStartupMessages(library(magrittr))
suppressPackageStartupMessages(library(GenomicRanges))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(ComplexHeatmap))
suppressPackageStartupMessages(library(universalmotif))

drake::r_make()
```

@@

In order to examine the properties of the E93 motif between different ChIP
peaks, we scan all E93 ChIP peaks for matches to the Fly Factor Survey E93 motif
using `runFimo()`. Results are returned as a GRanges object containing the
positions of each motif.

```{r}
e93_fimo <- runFimo(all_sequences, fly_factor_expressed$Eip93F_SANGER_10, thresh = 1e-3)
```

@@

This manuscript was automatically generated using Rmarkdown within the
`memes_docker` container. Its source code, raw data, and
instructions to reproduce all analysis can be found at
[github.com/snystrom/memes_paper/](github.com/snystrom/memes_paper/). Data used in this manuscript were from: [GSE141738](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE141738).
